Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex
beautifying

			For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\

@@

@@

Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously. Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

@@

		In an asynchronous system, the first DIT could happen before the arrival of at
		least one job of each task. We thus introduce the following notion:

		\begin{definition}
			The \textbf{first periodic DIT} of a system is the earliest DIT occurring
			strictly after the arrival of at least one job of each task.
		\end{definition}

@@

\begin{figure}[h]
$$
\begin{array}{|c|c|c|c|l}
   \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
   \text{period} & \text{period} & \text{period} & \text{period} & \\
  \hline
  t > 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
\end{array}
$$
\begin{center}
\caption{Behavior of an asynchronous system under EDF.}
\label{fig:asyncBehavior}
\end{center}
\end{figure}

>>>>

			For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). The equations are thus indeed linear.\\

@@

			\subsubsection{Removing redundancy}

@@

			Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously. Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to consider every interval $[0, t]$ with $t$ being a deadline before the first DIT.\\

@@

		In an asynchronous system, the first DIT may happen before $O_{max}$, i.e. before all tasks are in the system. We thus introduce the following notion:

		\begin{definition}
			The \textbf{first periodic DIT} of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{definition}

@@

\begin{figure}[h]
$$
\begin{array}{r||c|c|c|l}
    & \text{Incomplete} & \text{Transitive} & \text{Stationary} & \cdots \\
   \text{Name} & \text{period} & \text{period} & \text{period}  & \\
  \hline
  \text{size} & O_{max} & H & H & \cdots \\
  \hline
  t \geqslant & 0 & O_{max} & O_{max} + H & \cdots
\end{array}
$$
\begin{center}
\caption{Behavior of an asynchronous system under EDF.}
\label{fig:asyncBehavior}
\end{center}
\end{figure}
